Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-25 krs-survey.tex
Cleaned headers
Proof-reading of the first half of the paper

%\documentclass[twoside,a4paper]{report}
\documentclass[a4paper, twocolumn]{article}

@@

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{supertabular}
\usepackage{multirow}
\usepackage{varwidth}

\newcommand{\turn}[3][10em]{% \turn[<width>]{<angle>}{<stuff>}
  \rlap{\rotatebox{#2}{\begin{varwidth}[t]{#1}\bfseries#3\end{varwidth}}}%
  }

\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}
\fxsetup{footnote}
\fxsetup{nomargin}

\definecolor{codegray}{gray}{.95}
\definecolor{palegray}{gray}{.65}
\lstset{language=C,
	numbers=left,
	tabsize=2,
	basicstyle=\scriptsize,
	stringstyle=\textrm,
	showstringspaces=false,
	frame=none,
	xleftmargin=3pt,
	backgroundcolor=\color{codegray}}

@@

\newcommand{\concept}[1]{{\footnotesize \texttt{#1}}}
\newcommand{\ie}{{\textit{i.e.~}}}
\newcommand{\cf}{{\textit{cf~}}}
\newcommand{\eg}{{\textit{e.g.~}}}

\newcommand{\stmt}[1]{{\footnotesize \tt $\langle$ #1\relax$\rangle$}}
%\newcommand{\stmt}[1]{{\footnotesize $\langle$\stmttt#1\relax$\rangle$}}
\newcommand{\rawstmt}[1]{{\footnotesize \stmttt#1\relax}}
\def\stmttt#1 #2 #3\relax{{\tt#1} {\bf{\tt #2}} {\tt #3}}

\newcommand{\setstmt}[1]{{\footnotesize [\setstmttt#1\relax]}}
\def\setstmttt#1,#2\relax{\rawstmt{#1}, \rawstmt{#2}}

@@

The aim of this contribution is two-fold: we first propose a typology of
knowledge representation systems for service robotics that covers intrinsic
features like expressiveness or reasoning techniques as well as extrinsic
features like knowledge acquisition and integration into pre-existent robotic
architectures.

We then survey the current knowledge representation system in the community to
identify which knowledge-bound cognitive abilities are today well understood
and implemented, and which would require more efforts.

We hope this article may bring a clearer picture of the challenges of knowledge
representation and manipulation for the robotics research community.

@@

    Central to this effort is to develop an understanding of the relationship
    between the knowledge, the perception, and the action of \[...\] a robot. The
    sorts of questions we want to be able to answer are

@@

Those questions have in common one prerequisite to be answered: the robot must
be able to manipulate \emph{explicitly} knowledge, and hence, need a way to
represent the knowledge.

This survey focuses on this knowledge representation issue: we aims at first
establishing a as-exhaustive-as-possible typology of representation needs for
robotics, and then at painting the current landscape of approaches to the
knowledge representation problem in the research community, in order to
summarize the major trends and to identify the possible shortcomings.

@@

We have also tried, for each project, to make clear \begin{inparaenum} \item
how informations from perception or interaction are turned into knowledge,
\item how, in return, symbolic concept are \emph{anchored} into the robot
sensori-motor space, \item how the knowledge representation system integrates
with the decisional layers of the robot, and how this can improve or ease
robotic control.\end{inparaenum}

@@

Since this article discusses at length the concept of knowledge in the context
of robotics, it is useful to make our terminology explicit.  No general
agreement on a definition of ``knowledge'' exists. In our context, we call
``knowledge'' \emph{an explicit set of interrelated logical facts that are
meaningful to the robot executive controller} (by \emph{meaningful} we mean
that can possibly be interpreted to lead to a purposeful action).

The relation of \emph{data} and \emph{information} to knowledge is a debated
epistemology question (the interested reader is invited to refer to the
Wikipedia page on the ``DIKW'' hierarchy). In this article, we will associate
data to low-level material like raw sensor output, and information to
uncontextualized symbolic facts.

To give a example, image a human watching at a book and being tracked by a
Kinect sensor: the pose of the human skeleton in the world would be the data,
the fact \concept{looksAt(human, book)} as computed by a geometric reasoning
module would be the information, the fact \concept{looksAt(john,
war\_and\_peace)}, fully grounded and connected to the whole knowledge base of
the robot would be proper knowledge.

@@

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie , dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen (as described in
section~\ref{sect|scenario}).

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarily designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are able of on-line, dynamic knowledge acquisition and reasoning 
    (\ie not a simple static database).
\end{inparaenum}

@@

While classical cognitive architectures like {\sc Soar}~\cite{Lehman2006} or
{\sc ACT-R} have declarative knowledge modules~\cite{Derbinsky2010} and have
been recently used on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for
instance), they are also absent from this survey because we did not find much
references in the literature on knowledge manipulation and representation
applied to robotic scenarii in these architectures.

@@

To the extend of our knowledge, no previous published work attempt to build a
typology of cognitive abilities related to knowledge and required by service
robotics.

In a slightly broader context, Heintz et al.~\cite{Heintz2008} define
\emph{knowledge processing middlewares} as systems supporting ``declarative
specifications for flexible configuration and dynamic reconfiguration of
context dependent processing at many different levels of abstraction''. They
identify six characteristics: the system must be able to merge informations
from different, possibly distributed sources; it should support quantitative as
well as qualitative processing of information, it should offer bottom-up and
top-down processing, it should be able to deal with uncertainty, allow for
``flexible configuration and reconfiguration'' (which require what we call
\emph{non-monotonicity} in this article) and eventually Heintz et al. call for
meta-knowledge and introspective capacities (``declarative specification of the
processing functionalities''). In this paper, we focus our analysis on similar
system with however an emphasize on the symbolic capabilities.

Several surveys compare global cognitive architectures (\cite{Vernon2007, Chong2009}).
Vernon et al.~\cite{Vernon2007} split these architectures into two broad
categories: the \emph{cognitivist} ones (where cognition is considered as an
explicit computation problem, often based on symbol manipulation), and the
\emph{emergent} ones (where cognition only exists as a result of the
interaction of the system with its environment). The approaches presented in
this paper are, at a few exceptions, prototypical \emph{cognitivist} approaches
that aim at making knowledge explicit within the robot architecture. Vernon et
al. propose twelve \emph{characteristics of cognitive system} to compare
architectures. Amongst them, they mention the \emph{inter-agent epistemology} (how
the structure of the world is captured in a representation and shared), the
relation to \emph{embodiment}, the ability to \emph{anticipate} and to
\emph{adapt}, and the mechanisms of \emph{motivation}. While presented at the
level of the whole robotic architecture, these features also translate into
knowledge representation strategies and are relevant to our study.

At a broader scope, several authors from fields that are connected to robotics
have previously listed desirable features of artificial systems aiming at
cognitive abilities as rich as possible.

@@

Coming from the perspective of natural language processing in situated context,
Roy and Reiter, in~\cite{Roy2005}, summarize what they see as the main
challenges to be tackled by KRS: cross-modal representation systems, association of
words with perceptual and action categories, modeling of context, figuring out
the right granularity of models, integrating temporal modeling and planning,
ability to match past (learned) experiences with the current interaction and
ability to take into account the human perspective.

Knowledge representation systems in robotics are concerned by most, if not all,
of these points, and we shall reuse them later, in slightly reformulated ways.

@@

The next section proposes a prototypical scenario in a rich semantic
environment. We will not survey knowledge representation systems based on this
scenario: we merely use it to ground the selection and illustrate the set
features that define the dimensions of a
knowledge representation system for robotics.

@@

Section~\ref{sect|surveyed-systems} then presents each of the systems we
examined, and underlines their specificities.

We finally summarize in section~\ref{sect|summary} the current approaches in
relation to the previously identified set of features. This leads us to
identify several new research directions that are not sufficiently addressed by
the current state of the art.

@@

In order to illustrate what we consider to be the required features of a
knowledge representation system for robotics, we introduce in this section a
demonstration scenario.

While devising a scenario inevitably constraints the breadth of abilities we
examine, we insist on the fact that our main purpose here is to ground into a
real case the set of representational features we consider as desirable.  We
will \emph{not} evaluate any of the systems we survey in this article by
judging their applicability to this particular scenario.

We entitle our scenario ``the Brownie scenario'' (Fig.~\ref{fig|scenario}).

Robi and Roba are two service robots. They are considered to be able to freely
move and pick objects, but they are not expected to have the exact same
hardware and softwares architectures, and specially, they are not expected to
have the same knowledge representation system. These robots cooperate with a
human in a kitchen environment.

The main task of the scenario is the joint realization of a brownie, initiated
by the human injunction ``Let's make a brownie for tonight!''.

The scenario is successful if the task is achieved (the brownie is baked) and:

	\item it took less time that it would have require for the human alone,

	\item it didn't require a heavier cognitive involvement from the human that
	what would have been required without the robots' help.

@@

% Representation of a complex task
We can further refine these categories: to prepare and bake a brownie, the
robot first needs to make sense of the very term \emph{brownie}: what is it?
what is it used for? what is it made of? etc. We call this knowledge
\emph{common-sense knowledge} and the robot must be able not only to represent
it, but also to have some kind of access to it (for instance through a initial
set of facts that are made available at startup, or via access to a Web-based
knowledge base like Wikipedia, etc.)

Bound to the action \emph{make}, this should lead the robot to build and
represent a \emph{context}: we are in a scenario involving cooking. Actions
related to cooking often take place in the kitchen, cooking requires ingredients, 
utensils and a procedure that may be provided by a recipe, etc.

This last sentence implies several other features for our knowledge
representation system: ``cooking often takes place in the kitchen'' implies
that representation of both uncertainty and likelihood is desirable. The fact
that cooking is associated to a place further implies that the system models
locations and is able to attach \emph{thematic relations} to concept
(here, the likely location of the cooking action).

``cooking requires ingredients that may be provided by a recipe'' hints about a
very common feature available in most knowledge representation systems:
\emph{reasoning}. The robot \emph{infers} that cooking may require a recipe
since a list of ingredients is a pre-requisite of the cooking action, and a
recipe may provide such a list. If we omit the ``may'', this is a typical
example of first-order logic reasoning. Many other reasoning techniques exist
(including probabilistic ones -- ones able to deal with the ``may''), we shall
illustrate some of them later in this scenario.

@@

Procedures are in addition often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened to put the cake in the oven.
Such underspecification should be detectable, representable, and ideally
completable by the knowledge representation system\footnote{Note that we do not
assume here the {\it knowledge representation system} to be a single software
component: it may well be the result of the aggregation of several logical
components working together}.

@@

Cooperation in our scenario can intervene at many places. For instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. This \emph{helping} behaviour makes sense only if
the first agent knows that the recipient agent both needs the information but
does not know it. This in turn requires the robot to be able to model the
knowledge of the other agents: to think \emph{from the perspective} of another
agent (this idea is related to the so-called Theory of Mind~\cite{Leslie2000}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general~\cite{Jakobson1960} requires the addresser and the
addressee to share a common interpretative framework (a shared common-sense
knowledge -- or cultural background -- and a shared context). In our scenario,
the agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Behind the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this so-called \emph{grounding}
operation is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding usually denotes the {\it top-down}
operation: from the symbol to the percept. It is however commonly bundled with
the converse operation, that retrieve (or create) symbols from perception.

@@

In order to effectively share tasks, the robot must also know what it is
capable of: \emph{capability introspection} (both in term of general capability
and of immediate ability) is thus often desirable. More general introspection
(like the ability to tell ``who I am'' or ``what do I think of'' does not
appear to be necessary in our scenario. This may however be required in more
general human-robot interaction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Typology of Knowledge Representation Systems Requirements for Robotics}
\label{sect|features}

We presented an imaginary cooking scenario where numerous desirable
features for a knowledge representation system for robotics have been
identified in no particular order.

@@

@@

\subsubsection{Introduction: Main Logic Formalisms}

@@

A large number of logic formalism do exist, we shall summarize below the most
relevant for systems actually deployed in current robotic architectures.

@@

\emph{Horn clauses} are an important subset of FOL because the satisfiability
of a set of such clauses is a $P$-complete problem. A Horn clause is a
disjunction of literals (a \emph{clause}) with at most one positive literal:
$\neg p \vee \neg q \vee \cdots \vee \neg t \vee u$, which can also be
represented as $(p \wedge q \wedge \cdots \wedge t) \rightarrow u$.  Important
logic programming languages like Prolog are based on Horn clauses.

The family of \emph{Description Logics}~\cite{Baader2008} also play an
important role. It is also a subset of the first-order logic, with some
extensions in second-order logic. Description logics are notable because most
of them are known to be decidable. In description logic, axioms are build from
\emph{concepts}, \emph{roles} (that are unary or binary predicates) and
\emph{individuals}. The W3C OWL-DL standard is a widely-used language to
describe domains with the description logic.

Because Description Logics have been originally created from the perspective of
a \emph{knowledge representation language} and not a logic language, their
terminology (\emph{concept} or \emph{class}, \emph{role} or \emph{property},
\emph{individual},...) is well-suited to knowledge description and we may use
it in the remaining of this paper outside of the strict context of  Description
Logics.

\emph{Modal logic}, that allow for statement qualification like
\emph{possibility} or \emph{necessity}, have been shown to be closely related
to description logics. Modal logic allows to represent conveniently parallel
possible worlds and facts like ``the robot knows \emph{that the human knows}
how to read a recipe''.

@@

Note that most of these logic formalisms are still active research field by
their own, and practical considerations (especially the availability of
reasoners efficient enough for on-line use on a robot) often constraint the
choice of a logical formalism and a level of expressive power.

\paragraph{Some examples}

\emph{The robot knows that a blue bottle is laying on the table.}

\emph{The robot knows that the human knows about the position of the bottle,
but the robot does not know what the human actually know about it.}

@@

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle on a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
a simple, concrete example of consequences of the CWA/OWA choice on reasoning.

@@

Domains constrained with the closed world assumption lead to more tractable
inference problems, and allow for instance the use of logic languages like
Prolog. Thus, several approaches exists to \emph{locally close} a domain (\cf
Levesque~\cite{Levesque2008}, section 24.3.2 for a summary of those).

@@

As stated by Josyula and Raja, meta-cognition is composed of both
\emph{``meta-level control of cognitive activities and the introspective
monitoring of such activities to evaluate and to explain them"}.

A knowledge representation system endowed with \emph{meta-cognition} is not
only able to manipulate knowledge but also to exhibit and manipulate the
structure of its knowledge and the reasoning process. For instance, the ability
to explain a logical inconsistency in a KRS is a meta-cognitive function.
Sloman~\cite{Sloman2011}

@@

@@

\fxfatal{Discuss time chronicles~\cite{Ghallab1996}}

@@

\paragraph{The introspective robot}

@@

A particularly important aspect of introspection relates to the description of
its own capabilities: which sensors/actuators/computation services exist and
are currently available ?  While at a first level, these descriptions can be
static (\eg the robot has one laser scanner and two arms), at a second level,
the description is updated and reflect the current (and possibly past and
future) state of the robot. Note that these description may also involve
geometric descriptions (a kinematic chain, the pose of a device, etc.) that may
be deported outside of the main knowledge base. Efforts trying to formalize,
maintain and expose the capabilities and state of a robot are not new (and
ground themselves in work and techniques for self-descriptive remote procedure
calls in computing science), but take a renewed importance with applications
for high-level multi-robot cooperation. Recent work in that direction
include~\cite{Kunze2011}.

@@

Reasoners can then provide other type of inferences, like:

@@

        \item universal, existential and cardinality constraints (including \concept{allValue}, 
        \concept{someValue}, \concept{hasValue}),

        \item property characteristics (symmetry, transitivity, etc.)

@@

    \item set operations like: \par \footnotesize \concept{Color} $\equiv$ {\bf
    unionOf}(\concept{blue}, \concept{green}, \concept{orange},
    \concept{black}...) \normalsize

@@

\concept{Egg}$(a) \wedge $ \concept{Egg} $(b) \wedge $
\concept{MakeOmelette}$(a, b, c) \to \lnot $ \concept{Egg}$(a) \wedge \lnot $
\concept{Egg}$(b) \wedge $ \concept{Omelette}$(c)$

@@

One important exception is the \emph{negation as failure} inference rule, as
implemented by {\sc Prolog} for instance, that allows for non-monotonicity, but
only \emph{within the closed world assumption}.

@@

...seem to be mostly WIP...

>>>>

\documentclass[a4paper, twocolumn]{article}

@@

\usepackage{hyperref}
\usepackage{graphicx}

%tables
\usepackage{booktabs}
\usepackage{supertabular}
\usepackage{multirow}
\usepackage{varwidth}

\newcommand{\turn}[3][10em]{% \turn[<width>]{<angle>}{<stuff>}
  \rlap{\rotatebox{#2}{\begin{varwidth}[t]{#1}\bfseries#3\end{varwidth}}}%
  }
\usepackage{pdflscape} %% Used for very big table

\usepackage{paralist}

\usepackage[draft]{fixme}
\fxsetup{footnote}
\fxsetup{nomargin}

\newcommand{\ie}{{\textit{i.e.\ }}}
\newcommand{\cf}{{\textit{cf~}}}
\newcommand{\eg}{{\textit{e.g.\ }}}

% Macros related to concepts/statements typesetting
\newcommand{\concept}[1]{{\footnotesize \texttt{#1}}}
\newcommand{\stmt}[1]{{\footnotesize \tt $\langle$ #1\relax$\rangle$}}
\newcommand{\rawstmt}[1]{{\footnotesize \stmttt#1\relax}}
\def\stmttt#1 #2 #3\relax{{\tt#1} {\bf{\tt #2}} {\tt #3}}
\newcommand{\setstmt}[1]{{\footnotesize [\setstmttt#1\relax]}}
\def\setstmttt#1,#2\relax{\rawstmt{#1}, \rawstmt{#2}}

@@

@@

The aim of this contribution is two-fold: we first propose a typology of
knowledge representation systems for service robotics that covers intrinsic
features like expressiveness or reasoning techniques as well as extrinsic
features like knowledge acquisition and integration into pre-existent robotic
architectures. We base the typology on an initial typical scenario of service
robotics.

We then survey the current knowledge representation system in the community to
identify which knowledge-bound cognitive abilities are today well understood
and implemented, and which would require more research efforts.

We hope this article may bring a clearer picture of the challenges of knowledge
representation and manipulation for the robotic research community.

@@

    Central to this effort is to develop an understanding of the relationship
    between the knowledge, the perception, and the action of [\ldots] a robot. The
    sorts of questions we want to be able to answer are

@@

To be answered, those questions have in common one prerequisite: the robot must
be able to manipulate \emph{explicitly} knowledge, and hence, need a way to
represent the knowledge.

This survey focuses on this knowledge representation issue: we aims at first
establishing a as-exhaustive-as-possible typology of representation needs for
robotics in the specific context of service robotics, and then at painting the
current landscape of approaches to the knowledge representation problem in the
research community, in order to summarize the major trends and to identify the
possible shortcomings.

@@

We have also tried, for each project, to make clear \begin{inparaenum} \item
how informations from perception or interaction are turned into knowledge,
\item how, in return, symbolic concept are \emph{anchored} into the robot
sensori-motor space, \item how the knowledge representation system integrates
with the decisional layers of the robot, and how this can improve or ease
robotic control.\end{inparaenum}
\fxfatal{Do we really do it?}

@@

Since this article discusses at length the concept of knowledge in the context
of robotics, it is useful to make our terminology explicit.  No general
agreement on a definition of ``knowledge'' exists. For our needs, we call
``knowledge'' \emph{an explicit set of interrelated logical facts that are
meaningful to the robot's executive controller}, where \emph{meaningful} means
that it can possibly be interpreted to lead to a purposeful action).

The relation of \emph{data} and \emph{information} to knowledge is a debated
epistemology question (the interested reader is invited to refer to the
Wikipedia page on the ``DIKW'' hierarchy). In this article, we will associate
\emph{data} to low-level material like raw sensor output, and
\emph{information} to uncontextualized symbolic facts.

To give a example, imagine a human looking at a book while being tracked by a
Kinect sensor: the pose of the human skeleton in the world would be the data,
the fact \concept{looksAt(entity1, entity2)} as computed by a geometric reasoning
module would be the information, the fact \concept{looksAt(john,
war\_and\_peace)}, fully grounded and connected to the whole knowledge base of
the robot would be proper knowledge.

@@

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen (we will
describe such a scenario in section~\ref{sect|scenario}).

We have limited ourselves to systems that
\begin{inparaenum} 
    \item  run on \emph{service robot} (that is, robots that interact with 
    objects in a semantic-rich environment primarily designed for humans),
    \item  ground the knowledge in the physical world (physically embedded
    systems able to assess their environment),
    \item  are able to merge different knowledge modalities,
    \item  are able of on-line, dynamic knowledge acquisition and reasoning 
    (\ie not simple static databases).
\end{inparaenum}

@@

While classical cognitive architectures like {\sc Soar}~\cite{Lehman2006} or
{\sc ACT-R} have declarative knowledge modules~\cite{Derbinsky2010} and have
been recently used on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for
instance), they are also absent from this survey because we did not find much
references in the literature on knowledge manipulation and representation
applied to robotic scenarii for these architectures.

@@

To the extend of our knowledge, no previous published work attempt to build a
typology of cognitive abilities strictly related to knowledge in the context of
service robotics.

In a slightly broader context, Heintz et al.~\cite{Heintz2008} define
\emph{knowledge processing middlewares} as systems supporting ``declarative
specifications for flexible configuration and dynamic reconfiguration of
context dependent processing at many different levels of abstraction''. They
identify six characteristics: the system must be able to merge informations
from different, possibly distributed sources; it should support quantitative as
well as qualitative processing of information, it should offer bottom-up and
top-down processing, it should be able to deal with uncertainty, allow for
``flexible configuration and reconfiguration'' (which require what we call
\emph{non-monotonicity} in this article) and finally meta-knowledge and
introspective capacities (``declarative specification of the processing
functionalities''). In this paper, we focus our analysis on similar system with
however an emphasize on the symbolic capabilities.

Several surveys compare global cognitive architectures (\cite{Vernon2007, Chong2009}).
Vernon et al.~\cite{Vernon2007} split these architectures into two broad
categories: the \emph{cognitivist} ones (where cognition is considered as an
explicit computation problem, often based on symbol manipulation), and the
\emph{emergent} ones (where cognition only exists as a result of the
interaction of the system with its environment). The approaches presented in
this paper are, at a few exceptions, prototypical \emph{cognitivist} approaches
that aim at making knowledge explicit within the robot architecture. Vernon et
al. propose twelve \emph{characteristics of cognitive system} to compare
architectures. Amongst them, they mention the \emph{inter-agent epistemology} (how
the structure of the world is captured in a representation and shared), the
relation to \emph{embodiment}, the ability to \emph{anticipate} and to
\emph{adapt}, and the mechanisms of \emph{motivation}. While presented at the
level of the whole robotic architecture, these features also translate into
knowledge representation strategies and are relevant to our study.
\fxwarning{Detail Chong here}

At an even broader scope, several authors from fields that are connected to robotics
have previously listed desirable features of artificial systems aiming at
rich cognitive abilities.

@@

Coming from the perspective of natural language processing in situated context,
Roy and Reiter, in~\cite{Roy2005}, summarize what they see as the main
challenges to be tackled by KRS: cross-modal representation systems,
association of words with perceptual and action categories (\emph{grounding}),
modeling of context, definition of the right granularity of models, integration
of temporal modeling and planning, ability to match past (learned) experiences
with the current interaction and ability to take into account the human
perspective.

Knowledge representation systems in robotics are concerned by most, if not all,
of these points, and we shall indeed mention them in our typology, in slightly
reformulated ways.

@@

The next section proposes a prototypical scenario of a robot acting in a rich
semantic environment. We will not survey knowledge representation systems based
on this scenario: we merely use it to ground the selection and illustrate the
set of features that define the dimensions of a knowledge representation system
for robotics.

@@

Section~\ref{sect|surveyed-systems} then presents each of the systems we have
examined, and underlines their specificities.

We finally summarize in section~\ref{sect|conclusion} the current approaches in
order to identify several research directions that are not sufficiently
addressed by the current state of the art.

@@

In order to illustrate what we consider to be the required features of a
knowledge representation system for robotics, we introduce in this section an
(imaginary) demonstration scenario.

While devising a scenario inevitably constraints the breadth of abilities we
examine, we insist on the fact that our main purpose here is to ground into a
concrete case the set of representational features we consider as desirable.

We entitle our scenario ``the Brownie scenario'' (Figure~\ref{fig|scenario}):
Robi and Roba are two service robots, that can freely
move and pick objects around (with possibly different hardware and softwares
architectures, including different knowledge representation systems). They
cooperate with a human in a kitchen environment.

The main task of the scenario is the joint realization of a brownie, initiated
by the human: ``Let's make a brownie for tonight!''.

The scenario is successful if the task is achieved (the brownie is baked) in a
reasonable time (typically shorter than what it would have been required by the
human alone).

@@

% Representation of a complex task
We can further refine these categories: to prepare and bake a brownie, the
robot first needs to make sense of the term \emph{brownie} itself: what is it?
what is it used for? what is it made of? etc. We call this knowledge
\emph{common-sense knowledge} and the robot must be able not only to represent
it, but also to have access to an initial source (for instance through a initial
set of facts that are made available at startup, or via access to a Web-based
knowledge base like Wikipedia, etc.)

Once bound to the action \emph{make}, this should lead the robot to build and
represent a \emph{context}: we are in a scenario involving cooking. The context
enables the robot to retrieve more common-sense knowledge, like that actions
related to cooking often take place in the kitchen, cooking requires
ingredients, utensils and a procedure that may be provided by a recipe.

These last assertions imply several other features for our knowledge
representation system: ``cooking often takes place in the kitchen'' implies
that representation of both uncertainty and likelihood is desirable. The fact
that cooking is associated to a place further implies that the system models
locations and is able to attach \emph{thematic relations} to concept
(here, the likely location of the cooking action).

``cooking requires ingredients'' hints about another very common feature
available in most knowledge representation systems: \emph{reasoning}. The robot
can \emph{infers} that cooking may require a recipe since a list of ingredients
is a pre-requisite of the cooking action, and a recipe may provide such a list.
If we omit the ``may'', this is a typical example of first-order logic
reasoning. Many other reasoning techniques exist (including probabilistic ones
-- ones able to deal with the ``may''), we shall illustrate some of them later
in this scenario.

@@

Procedures are in addition often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened to put the cake in the oven.
Such underspecification should be detectable, representable, and ideally
completable by the knowledge representation system\footnote{Note that we do not
assume here the {\it knowledge representation system} to be a single software
component: it may well be the result of the aggregation of several logical
components working together. We come back later on this aspect.}.

@@

Cooperation in our scenario can intervene at many places. For instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. This \emph{helping} behaviour makes sense only if
the first agent knows that the recipient agent both needs the information but
does not know it. This in turn requires the robot to be able to model the
knowledge of the other agents: to think \emph{from the perspective} of another
agent (an idea that is related to the availability of a theory of
mind~\cite{Leslie2000}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general requires the addresser and the addressee to share a
common interpretative framework (a shared common-sense knowledge -- or cultural
background -- and a shared context)~\cite{Jakobson1960}. In our scenario, the
agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Behind the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this so-called \emph{grounding}
operation is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding is a bidirectional process: in
covers the {\it top-down} operation (from the symbol to the percept) and the
{\it bottom-up} converse (retrieval or creation of symbols from perception).

@@

In order to effectively share tasks, the robot must also know what it is
capable of: \emph{capability introspection} (both in term of general capability
and of immediate ability) is thus often desirable. More general introspection
(like the ability to tell ``who I am'' or ``what do I think of'') does not
appear to be necessary in our scenario. This may however be required in more
general human-robot interaction.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Typology of Knowledge Representation Requirements for Robotics}
\label{sect|features}

We now want to organize requirements from this imaginary cooking scenario where
numerous desirable features for a knowledge representation system for robotics
have been identified without any particular order.

@@

As previously mentioned, we propose six main categories.
\fxfatal{figure taxonomy}

@@

\subsubsection{Main Logic Formalisms}

@@

A large number of logic formalism do exist, we shall summarize below the most
relevant ones for systems actually deployed in current robotic architectures.

@@

\emph{Horn clauses} are an important subset of FOL because the satisfiability
of a set of such clauses is a $P$-complete problem (\ie practically tractable).
A Horn clause is a disjunction of literals (a \emph{clause}) with at most one
positive literal: $\neg p \lor \neg q \lor \cdots \lor \neg t \lor u$, which
can also be represented as $(p \land q \land \cdots \land t) \rightarrow u$.
Important logic programming languages like Prolog are based on Horn clauses.

The family of \emph{Description Logics}~\cite{Baader2008} also play an
important role. It is also a subset of the first-order logic, with some
extensions in second-order logic. Description logics are notable because most
of them are known to be decidable (but not always in a practically tractable
manner). In description logic, axioms are build from \emph{concepts},
\emph{roles} (that are unary or binary predicates) and \emph{individuals}. The
W3C OWL-DL standard is a widely-used language to describe domains with the
description logic.

Because Description Logics have been originally created from the perspective of
a \emph{knowledge representation language} and not a logic language, their
terminology (\emph{concept} or \emph{class}, \emph{role} or \emph{property},
\emph{individual},\ldots) is well-suited to knowledge description and we may use
it in the remaining of this paper outside of the strict context of  Description
Logics.

\emph{Modal logic}, that allow for statement qualification like
\emph{possibility} or \emph{necessity}, have been shown to be closely related
to description logics~\cite{Baader2001}. Modal logic allows to represent conveniently parallel
possible worlds and facts like ``the robot knows \emph{that the human knows}
how to read a recipe''.

@@

Note that most of these logic formalisms are still active research field on
their own, and practical considerations (especially the availability of
reasoners efficient enough for on-line use on a robot) often constraint the
choice of a logical formalism and a level of expressive power.

@@

This distinction is important in robotics were the robot may have to manipulate
concepts with only partial knowledge on them. For instance, let imagine a robot
that sees a bottle on a table, whose bottom is hidden by another object. The
robot can not prove that the bottle is indeed \emph{on} the table. A knowledge
representation system relying on the closed world assumption would then assume
the bottle is \emph{not} on the table ($\lnot R^{CWA}_{isOn}(bottle, table)$)
whereas with the open world assumption, the proposition $R^{OWA}_{isOn}(bottle,
table)$ would be undecided. Example in table~\ref{table|cwa-owa-example} provides
another example of consequences of the CWA/OWA choice on reasoning.

@@

The OWL language is specifically known to assume an open world.  Domains
constrained with the closed world assumption lead to more tractable inference
problems, and allow for instance the use of logic languages like Prolog. Thus,
several approaches exists to \emph{locally close} a domain (\cf
Levesque~\cite{Levesque2008}, section 24.3.2 for a summary of those).

@@

As stated by Cox and Raja~\cite{Cox2007}, meta-cognition is composed of both
\emph{``meta-level control of cognitive activities and the introspective
monitoring of such activities to evaluate and to explain them"}.

A knowledge representation system endowed with \emph{meta-cognition} is not
only able to manipulate knowledge but also to exhibit and manipulate the
structure of its knowledge and the reasoning process. For instance, the ability
to explain a logical inconsistency in a KRS is a meta-cognitive function.
Sloman~\cite{Sloman2011} \fxfatal{...Sloman?}

@@

Thematic roles

@@

\fxfatal{Discuss time chronicles~\cite{Ghallab1996}}
\fxfatal{Discuss Allen intervals}

@@

\paragraph{Introspection}

@@

A particularly important aspect of introspection relates to the description of
its own capabilities: which sensors/actuators/computation services exist and
are currently available ?  While at a first level, these descriptions can be
static (\eg the robot has one laser scanner and two arms), at more advanced
levels, the description is updated and reflect the current (and possibly past
and future) state of the robot. Note that these description may also involve
geometric descriptions (a kinematic chain, the pose of a device, etc.) that may
be deported outside of the main knowledge base. Efforts trying to formalize,
maintain and expose the capabilities and state of a robot are not new (and
ground themselves in work and techniques for self-descriptive remote procedure
calls in computing science), but take a renewed importance with applications
for high-level multi-robot cooperation. Recent work in that direction
include~\cite{Kunze2011}.

@@

Reasoners can often provide other type of inferences, like:

@@

        \item universal, existential and cardinality constraints,

        \item property characteristics (inverse, symmetry, transitivity, etc.)

@@

    \item set operations like: \par \footnotesize \concept{Color} $\equiv \bigcup$ (\concept{blue}, \concept{green}, \concept{orange},
    \concept{black}, \ldots) \normalsize

@@

\concept{Egg}$(a) \land $ \concept{Egg} $(b) \land $
\concept{MakeOmelette}$(a, b, c) \to \lnot $ \concept{Egg}$(a) \land \lnot $
\concept{Egg}$(b) \land $ \concept{Omelette}$(c)$

@@

One important exception is the \emph{negation as failure} inference rule, as
implemented by {\sc Prolog} for instance, that allows for non-monotonicity
within the closed world assumption.

@@

\ldots seem to be mostly WIP\ldots
